How to select predictive models for decision-making or causal inference?

### 2023-12-16 how_to_select_causal_models.tex
One column

\documentclass[10pt,twocolumn]{article}

\usepackage[a4paper, left=15mm, right=15mm, top=20mm,]{geometry}
% declared functions and additional packages
\usepackage{caption}
\usepackage{subcaption}
\usepackage{threeparttable}
\usepackage{times}
\usepackage{hyperref}
\def\mycitecolor{green!50!black}
\def\mylinkcolor{red!60!black}
\hypersetup{ colorlinks=true, linkcolor=\mylinkcolor, citecolor=\mycitecolor }
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb} %mathbb packages
\usepackage{siunitx}
\usepackage{algorithm, algorithmicx, algpseudocode}
\usepackage{multirow}
\usepackage[sorting=nyt,style=numeric, natbib=true,doi=false,isbn=false,url=false,eprint=false, maxnames=999, maxcitenames=2]{biblatex} 
\DeclareNameAlias{default}{last-first}
\usepackage{placeins}
% associated arxiv class
%\usepackage{arxiv}
\usepackage{multicol}
\setlength{\columnsep}{0.5cm}
\usepackage{wrapfig}
%\usepackage{wraptable}
\usepackage{authblk}% for author affiliations
\usepackage[dvipsnames]{xcolor}

@@

\twocolumn
\section{Introduction}\label{sec:intro}

@@

\begin{figure}[h!]
    %\centering
    {\sffamily\footnotesize\scalebox{1.03}{a) Random forest, good average prediction but bad
            causal inference}}

@@

    \hfill%
    \includegraphics[width=1\linewidth]{images/toy_tlinear_model_small_R2_small_tau_risk.pdf}%

@@

\begin{figure}[h!]
    \includegraphics[width=\linewidth]{images/estimation_procedure_causal_selection_procedure.png}
    \caption{Estimation procedure for causal model
        selection.}\label{problem:estimation_procedure:figure}
\end{figure}

@@

\begin{figure}[!b]
    \centering
    \includegraphics[width=\linewidth]{images/_1_r_risk_domination_r_risk_domination__ref_metric_mean_risks_by_Dataset_feasible_only.pdf}
    %\hfill
    \caption{\textbf{The $R$-risk is the best metric}: Relative Kendall's $\tau$ agreement with $\tau\text{-risk}$.
        Strong and Weak overlap correspond to the first and last tertiles of the overlap distribution measured with
        Normalized Total Variation eq. \ref{eq:ntv}. \ref{apd:experiments:additional_results} presents the same results
        by adding semi-oracle risks in Figure \ref{apd:fig:relative_kendalls_all_datasets_all_metrics}, measured with
        absolute Kendall's in Figure \ref{apd:fig:all_datasets_tau_risk_ranking_agreement} and with $\tau\mathrm{-risk}$
        gains in Figure \ref{apd:all_datasets_normalized_bias_tau_risk_to_best_method}. Table
        \ref{apd:table:relative_kendalls_all_datasets} gives median and
        IQR of the relative Kendall.}\label{fig:relative_kendalls_all_datasets}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\linewidth]{images/_2_overlap_influence_overlap_by_bin_comparaison_kendall_by_Dataset_r_risk_only_twocols.pdf}
    %\hfill
    \caption{\textbf{Model selection is harder for low population
            overlap}:
        Kendall's $\tau$ agreement with $\tau\text{-risk}$. Strong, medium and Weak overlap
        are the tertiles of the overlap measured with NTV eq. \ref{eq:ntv}. \ref{apd:experiments:additional_results} presents results for all
        metrics in Figure \ref{apd:fig:all_datasets_overlap_effect} in absolute
        Kendall's and continuous overlap values in Figure
            {\ref{apd:fig:all_datasets_tau_risk_ranking_agreement}}.}\label{fig:all_datasets_overlap_effect_r_risk}
\end{figure}

@@

\begin{figure}[!tb]
    \includegraphics[width=\linewidth]{images/_3_procedure_r_risk_only_3datasets_twocols.pdf}

@@

\begin{figure}[!tb]
    \includegraphics[width=\linewidth]{images/_4_nuisance_models_r_risk_only_3datasets_twocols.pdf}

>>>>

% XXX: for submission
%\documentclass[10pt,twocolumn]{article}
\documentclass[11pt]{article}

%\usepackage[a4paper, left=15mm, right=15mm, top=20mm,]{geometry}
% XXX: for submission
\usepackage[a4paper, left=25mm, right=25mm, top=20mm,]{geometry}
% declared functions and additional packages
\usepackage{caption}
\usepackage{subcaption}
\usepackage{threeparttable}
\usepackage{times}
\usepackage{hyperref}
\def\mycitecolor{green!50!black}
\def\mylinkcolor{red!60!black}
\hypersetup{ colorlinks=true, linkcolor=\mylinkcolor, citecolor=\mycitecolor }
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb} %mathbb packages
\usepackage{siunitx}
\usepackage{algorithm, algorithmicx, algpseudocode}
\usepackage{multirow}
\usepackage[sorting=nyt,style=numeric, natbib=true,doi=false,isbn=false,url=false,eprint=false, maxnames=999, maxcitenames=2]{biblatex} 
\DeclareNameAlias{default}{last-first}
\usepackage{placeins}
% associated arxiv class
%\usepackage{arxiv}
\usepackage{multicol}
\setlength{\columnsep}{0.5cm}
\usepackage{wrapfig}
%\usepackage{wraptable}
\usepackage{authblk}% for author affiliations
\usepackage[dvipsnames]{xcolor}

@@

% XXX: for submission
%\twocolumn
\section{Introduction}\label{sec:intro}

@@

\begin{figure}[h!]
    % XXX: for submission
    \centering\begin{minipage}{.6\linewidth}
    {\sffamily\footnotesize\scalebox{1.03}{a) Random forest, good average prediction but bad
            causal inference}}

@@

    \hfill%
    \includegraphics[width=1\linewidth]{images/toy_tlinear_model_small_R2_small_tau_risk.pdf}%
    \end{minipage}

@@

\begin{figure}[h!]
    % XXX: for submission
    \centering\begin{minipage}{.6\linewidth}
    \includegraphics[width=\linewidth]{images/estimation_procedure_causal_selection_procedure.png}
    \end{minipage}
    \caption{Estimation procedure for causal model
        selection.}\label{problem:estimation_procedure:figure}
\end{figure}

@@

\begin{figure}[!b]
    % XXX: for submission
    \centering\begin{minipage}{.75\linewidth}
    \includegraphics[width=\linewidth]{images/_1_r_risk_domination_r_risk_domination__ref_metric_mean_risks_by_Dataset_feasible_only.pdf}
    \end{minipage}
    \caption{\textbf{The $R$-risk is the best metric}: Relative Kendall's $\tau$ agreement with $\tau\text{-risk}$.
        Strong and Weak overlap correspond to the first and last tertiles of the overlap distribution measured with
        Normalized Total Variation eq. \ref{eq:ntv}. \ref{apd:experiments:additional_results} presents the same results
        by adding semi-oracle risks in Figure \ref{apd:fig:relative_kendalls_all_datasets_all_metrics}, measured with
        absolute Kendall's in Figure \ref{apd:fig:all_datasets_tau_risk_ranking_agreement} and with $\tau\mathrm{-risk}$
        gains in Figure \ref{apd:all_datasets_normalized_bias_tau_risk_to_best_method}. Table
        \ref{apd:table:relative_kendalls_all_datasets} gives median and
        IQR of the relative Kendall.}\label{fig:relative_kendalls_all_datasets}
\end{figure}

@@

\begin{figure}[!h]
    % XXX: for submission
    \centering\begin{minipage}{.75\linewidth}
    \includegraphics[width=\linewidth]{images/_2_overlap_influence_overlap_by_bin_comparaison_kendall_by_Dataset_r_risk_only_twocols.pdf}
    \end{minipage}
    \caption{\textbf{Model selection is harder for low population
            overlap}:
        Kendall's $\tau$ agreement with $\tau\text{-risk}$. Strong, medium and Weak overlap
        are the tertiles of the overlap measured with NTV eq. \ref{eq:ntv}. \ref{apd:experiments:additional_results} presents results for all
        metrics in Figure \ref{apd:fig:all_datasets_overlap_effect} in absolute
        Kendall's and continuous overlap values in Figure
            {\ref{apd:fig:all_datasets_tau_risk_ranking_agreement}}.}\label{fig:all_datasets_overlap_effect_r_risk}
\end{figure}

@@

\begin{figure}[!tb]
    % XXX: for submission
    \centering\begin{minipage}{.75\linewidth}
    \includegraphics[width=\linewidth]{images/_3_procedure_r_risk_only_3datasets_twocols.pdf}
    \end{minipage}

@@

\begin{figure}[!tb]
    % XXX: for submission
    \centering\begin{minipage}{.75\linewidth}
    \includegraphics[width=\linewidth]{images/_4_nuisance_models_r_risk_only_3datasets_twocols.pdf}
    \end{minipage}
